\chapter{Introduction}\label{sec:intro}
With the explosive image resources people uploaded every day, image recognition becomes a very hot topic and has draw many attentions in recent years. Every year, there are many inspiring results in the ImageNet Large Scale Visual Recognition Challenge (ILSVRC). 
With development of recognition technology, many IT companies want to use the image recognition techniques to serve their customers and many interesting applications have been developed, such as HowOld from Microsoft and Im2Calories from Google.

In order to successfully capture the diversity of different objects around us, many recognition models contain thousands or sometimes even millions of parameters and require large amount of training images to tune these parameters as well.
As the visual recognition system become increasingly successful in many general recognition tasks, people wish that it can solve the recognition problems in many new and complicated areas which are paid less attention to before.  
Unfortunately, for some real applications, it is often difficult and cost to collect large set of training images. Moreover, most algorithms require that the training examples should be aligned with a prototype, which is commonly done by hand. In many real applications, collecting and fully annotating these images can be extremely expensive and could have a significant impact on the over cost of the whole system.
Therefore, the biggest challenge of applying the current recognition algorithms to the new task is lacking of training data.
% As a result, the challenges come from two aspects
%\begin{enumerate}
%	\item Abundant new categories/scenario. In some tasks, it is required for the system to learn new categories or scenarios. The recognition algorithm should be more dynamic to adapt the new categories and scenarios.
%	\item Lack of the training images. As these tasks are lack of attention before, the training data is rare. The annotation process of these data could be both expensive and time-consuming. 
%\end{enumerate} 

On the other hand, object recognition is one of the most important part of our human visual system. We can recognize various kinds of materials (apple, orange, grape), objects (vehicles, buildings) and natural scenes (forests, mountain). At the age of six, human can recognize about $10^4$ object categories\cite{biederman1987recognition}. 
Our human can learn and recognize a new object with just a glance, which means we can capture the diversity of forms and appearances of a objects with just a handful examples. This remarkable ability is obtained by effectively leveraging the learned knowledge and applying it to the new tasks. It could be ideal if there is a visual recognition model can have such ability, which is referred to as \textbf{Visual Transfer Learning} (VTL). 

VTL has been increasing popular with the success of modern image recognition algorithms. In VTL, the source domain is referred to the one we have already learned and the target domain is the one we actually want to learn. In VTL, measuring the relatedness of the source and target tasks is important for the transfer process.
In previous studies of VTL, people assume that the source data are always available and can be freely accessed. Therefore, the relatedness of the source and target domain can be effectively measured by comparing the data in two domains using some statistics. However, this assumption is rarely hold in real applications. Source data are often a subject of legal, technical and contractual constraints between data owners and data customers. Beyond privacy and disclosure obligations, customers are often reluctant to share their data. %\hl{When operating customer care, collected data may include information on recent technical problems which is a highly sensitive topic that companies are not willing to share.}
On the other hand, sharing the model trained from the source data, i.e. the source model, instead of the data can avoid these obligations and is more common in real applications. VTL under this situation is usually called \textbf{Hypothesis Transfer Learning} (HTL) \cite{kuzborskij2013stability} and the source model is called hypothesis.

In this thesis, we investigate the VTL problem under the HTL setting. Specifically, we investigate the VTL problem under two settings: domain adaptation (transductive transfer) and learning the new categories (inductive transfer). The methods proposed in this thesis focus on how to leverage the knowledge from the source model and transfer it to the target task effectively. In this section, we first give an overview for image recognition. Then we illustrate the current approach for VTL tasks and their limitation for the real applications. Finally, we briefly demonstrate the contributions of this thesis. 

\section{Overview for Image Recognition}\label{sec:intro:over}
\input{introduction/overview.tex}
\section{Approaches in Visual Transfer Learning and the Limitations}
\input{introduction/senario.tex}
\section{Main Contribution}
\input{introduction/limits}
\section{Summary}
In this chapter, we briefly introduced the problems that are solved in this thesis. We first demonstrate the procedure for image recognition and introduce some previous work for visual transfer learning. Then we pointed out the limitations of the previous work and briefly introduced our methods.